Portfolio conservation of metapopulations\\under climate change

### 2013-08-26 inst/ms/ms.tex
Updates to ms; wrap ms

@@

\setlength{\parskip}{6pt} \setlength{\parindent}{0cm}

Sean C. Anderson\textsuperscript{1*}, Jonathan W. Moore\textsuperscript{1}, Trevor A. Branch?, Nicholas K. Dulvy\textsuperscript{1}, Michelle M. McClure?, Andrew B. Cooper\textsuperscript{2} (Authors and order to be discussed)

@@

\setlength{\parskip}{2pt} \setlength{\parindent}{16pt}

@@

A diversified financial portfolio reduces risk by exploiting the covariance between assets --- ideally one stocks rises while another one falls --- and there are two key mechanisms that generate asynchrony in metapopulation dynamics. First, localized habitat features can filter the environment generating unique conditions for subpopulations \citep{schindler2008, rogers2008} (\emph{senu} the Moran effect). For salmon, this mechanism acts primarily during freshwater life-history stages and since many salmon species spend considerable time in the ocean \citep{quinn2005}, a second mechanism is also of key importance --- diversity of response to a shared environment \citetext{\citealp[i.e.~response diversity,][]{elmqvist2003}; \citealp[and biocomplexity][]{colwell1998}; \citealp{hilborn2003}}. This second mechanism can result from unique phenotypic or genetic traits \citep{crozier2008, kovach2012} and be derived from rapid contemporary adaption \citep{stockwell2003, fraser2011} or long-term evolution to historical conditions \citep{eliason2011}. In this paper we focus on this latter, response-diversity mechanism, and evaluate it in the context of thermal response diversity.

Salmon are strongly affected by climate warming and yet show a remarkable diversity of tolerance to temperature \citep{beacham1989, crozier2006, battin2007, crozier2008}. In addition to climate warming posing perhaps the greatest threat to global biodiversity \citep{thomas2004}, warming poses a particular threat to riverine species whose ranges are largely confined to existing habitat \citep{thomas2010} and where shallower water, compared to larger water basins, can be affected more rapidly by thermal changes \citep{isaak2010} and by snow-melt timing and extreme hydrological events \citep{crozier2008}. These consequences, and in particular warmer water itself, can combine to limit salmon productivity through, for example, oxygen limitation \citep{portner2007} leading to decreased cardiac performance \citep{eliason2011} and having profound implications for behaviour \citep{goniea2006}, disease resistance \citep{crozier2008}, and energetic costs in general \citep{rand1998}, and ultimately survival \citep{peterman1998, eliason2011}. With 29\% of Pacific Northwest salmon populations having gone extinct since Euro-American contact \citep{gustafson2007}, these populations are at risk from any further decline in fitness \citep{mcclure2003}. Yet, adverse stream temperatures are already impeding recovery of some PNW salmon populations \citep{mccullough1999}.

@@

\noindent where $i$ represents a population, $t$ a generation time, $R$ the number of returns, $S$ the number of spawners, $a$ the productivity parameter (which can vary with the environment), and $b$ the density-dependent term (which is used as the asset weights in the portfolios). The term $w_{i(t)}$ represents first-order autocorrelated error. Formally, $w_{i(t)} = w_{ti-1} \rho_w + r_{i(t)}$, where $r_{i(t)}$ represents independent and normally distributed error with mean 0 and standard deviation of $\sigma_r$ (0.3; we include the base values in parentheses after relevant parameters). The parameter $\rho_w$ (0.4) represents the correlation between residuals from subsequent generations.

@@

\noindent where $W_i$ controls the width of the curve for population $i$, $e_t$ represents the environmental value at generation $t$, $e_i^{\mathrm{opt}}$ represents the optimal temperature for population $i$, and $a_i^{\mathrm{max}}$ represents the maximum possible $a$ value for population $i$. We set the $W_i$ parameters (evenly spaced values increasing and decreasing between 0.05 and 0.02) and calculated the $a_i^{\mathrm{max}}$ parameters so that the area under each curve was equal (30 units). We chose parameter values such that some populations were warm-tolerant, some were cold-tolerant, and some had a wider range of thermal-tolerance, but a lower maximum productivity (see Fig.~2a). Although we refer to a thermal-tolerance curve because temperature is a dominant driver of salmonid performance \citep{mccullough1999}, our model applies to any environmental tolerance (e.g.~tolerance to stream flow volume or changes in snow melt timing \citep{crozier2008}).

@@

\noindent where $R_{j(t)}$ is the number of returning salmon at generation $t$ whose natal stream was stream $j$. The subscript $k$ represents a stream ID and $n$ the number of populations. The denominator is a normalizing constant to ensure the desired fraction of fish stray. See Figure \ref{f:stray} for an example straying matrix.

Our simulation did not account for the homogenization of diversity due to straying. For example, all salmon in population A maintained the same thermal-tolerance curve regardless of how many salmon it received from population B. However, the low straying rates in our simulation rate should render this effect minimal except for populations at low abundance. In our model, the main implication is that, in reality, populations that reach a low abundance may reach demographic extinction, potentially suffer consequences such as inbreeding depression \citep{wang2002} and subsequently contribute little to response diversity.

@@

\noindent where $A$ represents the return abundance and $a$ and $b$ represent the Ricker model parameters. We included implementation uncertainty in the actual harvest rate $H_{\mathrm{act}}$ as

@@

\noindent where $\alpha_h$ and $\beta_h$ are the location and shape parameters in a beta distribution. They can be calculated from the desired mean $H_{\mathrm{tar}}$ and standard deviation $\sigma_h$ (0.05) as \citep[p.~97]{morgan1990}

@@

\noindent Further, to establish a range of spawner-return values and to mimic the start of an open-access fishery, for the first 30 years we drew the fraction of fish harvested randomly from a uniform distribution between 0.1 and 0.9. We discarded these initial 30 years as a burn-in period.

@@

\noindent where $e_t$ represents the environmental value in generation $t$ and $d$ represents normally distributed deviations of mean 0 and standard deviation $\sigma_d$ (2). We represented long-term environmental dynamics as a linear shift in the environmental value through time

@@

\noindent where $\beta_e$ (0.114) represents the slope. To maintain a balanced response, we centered the trend by subtracting the mean $\overline{\beta_e t}$ so that midway through the simulation (after any burn-in period) the environmental value was at the mean environmental tolerance.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Conserve an even sampling of response diversity.
\item
  Conserve the middle section of the metapopulation (conserve stable populations).
\item
  Conserve the lower half of the metapopulation (conserve cool-tolerant populations).
\item
  Conserve the upper half of the metapopulation (conserve warm-tolerant populations).
\end{enumerate}

@@

@@

Our simulation model emphasizes the importance of thinking at the portfolio level --- considering aggregate risk and performance for ecological portfolios. Although our results may appear intuitive, we often don't often consider aggregate risk and only by simultaneously considering aggregate risk and return can we optimally diversify ecological systems \citep{ando2012}. Thus we can think of portfolio risk-return performance as another dimension of conservation. This dimension emphasizes the value of a broader scale of management and focussing not just on currently productive populations but also on less productive populations to reduce long-term aggregate risk \citep[e.g.][]{hilborn2003, price2008}. This perspective does not negate an understanding at a finer scale, say of individual fish stocks. Rather, as in finance, it requires both an understanding of stock performance and an assessment of their covariance to predict properties of the portfolio as a whole.

THE FOLLOWING PARAGRAPH IS STILL BEING PIECED TOGETHER

Our findings support the existence of and inform the implementation of a number of existing guidelines and management structures for PNW salmonids. In the US, Evolutionarily Significant Units (ESUs) represent salmon populations that are reproductively isolated with an evolutionary heritage \citep{waples1991, moritz1994} and finer-scale Viable Salmonid Populations (VSPs) represent groups of fish that spawn in a given lake or stream in a particular season \citep{mceacheran2000}. In Canada, the rough equivalent to the ESU is a Conservation Unit (CU) as defined in the Wild Salmon Policy \citep{dfo2005wsp}. A CU consists of a group of salmon that are reproductively isolated and that if lost would be unlikely to recolonize in a reasonable time frame \citep{dfo2005wsp}. Both the US and Canadian guidelines recognize still-finer-scale population structure. We suggest that a salmon portfolio in our model could represent an ESU or CU and that the lessons learned from our models are thus directly applicable to management guidelines in the PNW.

VSP guidelines \citep{mceacheran2000} suggest\ldots{}

\begin{itemize}
\item
  maintaining diversity of a variety of forms to buffer against short-term environmental changes and adaptation to long-term environmental changes
\item
  conservation efforts should not focus exclusively where there is currently an abundance of salmon
\item
  metapopulation (multiple populations with some exchange) are important to maintain
\item
  some should be close for straying, but some should be far apart to reduce risk from sudden environmental change
\item
  important to incorporate uncertainty of ESU-level processes into assessments
\end{itemize}

CU guidelines \citep{dfo2005wsp} suggest\ldots{}

-

Our recommendations support a number of VSP and CU guidelines. For example, VSP guidelines suggest\ldots{} and the first objective of CU\ldots{} Therefore, we suggest an ESU or CU could represent a salmon portfolios and the lessons learned from models such as ours are directly applicable to management guidelines in the PNW.

END IN PROGRESS TEXT

Our model is unique in that it is the first to consider risk for metapopulations as a whole while identifying the role of response diversity in buffering risk. Our model follows from the work of \citet{cooper1999} who showed the importance of metapopulation habitat structure for salmonid conservation and \citet{moore2010} who linked salmon portfolio performance to asynchrony in population dynamics. Our model complements existing simulation-based salmon-habitat prioritization models that emphasize detailed assessment of individual stocks and we compare two of them here. One a frequently used simulation-based habitat-prioritization model, the Shiraz model \citep{scheuerell2006}, focuses on detailed conditioning of the habitat-population-dynamics relationship for a single salmon population. While the Shiraz model can be applied to an entire watershed it combines the populations together as a single unit. In contrast to our model, the Shiraz model breaks the spawner-recruit model into multiple stages. A second prioritization scheme proposes using population viability analysis (PVA) or surrogate measures of population viability combined with an assessment of the genetic consequences of losing various populations \citep{allendorf1997}. \citet{allendorf1997}, however, also focus on the assessment of individual stocks without considering their covariance and therefore the performance of the salmon portfolio as a whole. Compared to these detailed population-specific models, our model is at this stage primarily conceptual, but could be conditioned on real systems or expanded to incorporate greater life-stage realism. Our intention was to develop a parsimonious model to explore the salient aspects of metapopulation-portfolio performance.

We suggest a number of specific extensions to our simulation model. First our model could be extended beyond thermal response diversity. For salmon this might include response diversity to interdecadal climate signals such as the Pacific Decadal Oscillation \citep{mantua2002}, or to stream flow and dissolved oxygen \citep{priede1988}. Second, our model could be extended to metapopulations of other taxa, to ecological communities (after accounting for species interactions), or to meta-communities. Third, an extension of our model would consider the Moran or environmental-filter concept \citep{schindler2008, rogers2008} where populations experience increasingly different environmental forces at further distances. Fourth, a model could consider the contribution of contemporary evolution \citep{stockwell2003}. This rapid adaptation to changes in the environment could strongly affect portfolio performance and emphasizes the importance of maintaining genetic diversity. Finally, our model could be conditioned on a system of interest --- a particular river basin for example --- and the management metapopulation portfolio could be optimized across conservation and restoration options as part of a formal decision analysis.

@@

In conclusion, our results demonstrate the utility of considering metapopulations in a portfolio context and the power of portfolio simulation to consider robust management strategies that minimize metapopulation risk and maximize growth under uncertain environmental conditions. Our findings show that response diversity buffers metapopulation risk given short-term environmental stochasticity and ensures persistence given longterm regime changes. Further, our findings show that, independent of response-diversity, conserving more populations buffers metapopulation risk. These results point to the critical importance of choosing management, conservation, and restoration actions that preserve and promote response diversity and are robust to our uncertainty about response diversity distribution and future climatic conditions.

@@

\setlength{\parskip}{6pt} \setlength{\parindent}{0cm} \includegraphics[height=5.5in]{../examples/simulation-diagram3.pdf}

@@

\clearpage
\includegraphics[width=3.0in]{../examples/thermal-curve-scenarios.pdf}

@@

\clearpage
\includegraphics[width=4.0in]{../examples/spatial-arma-sim.pdf}

@@

\clearpage
\includegraphics[width=5.0in]{../examples/spatial-mv.pdf}

@@

\clearpage
\includegraphics[width=5.0in]{../examples/cons-plans-n.pdf}

>>>>

Overall thoughts and notes:

\begin{itemize}
\item
  The introduction may be a bit literature heavy. (We also need to cut 11 references to get to 50.)
\item
  The main message may be a bit repetitive throughout.
\item
  I wish I didn't have so many paragraphs with numbered lists, but am struggling to work around that.
\item
  I think there is room for expansion of the discussion (we still have \textasciitilde{}500 words to play with). The discussion could benefit from bringing in more concrete examples of how this ties in with PNW salmon.
\item
  The supplementary figures and captions aren't finished but should be quick to generate.
\item
  I will write a short vignette describing how to use the R package like I did for the Methods in Ecology and Evolution paper.
\item
  I will submit the \texttt{.pdf} version; the \texttt{.docx} version is for you to edit with Track Changes, if you'd like. Only the \texttt{.pdf} version contains the figures and if you can't see the equations in the \texttt{.docx} version (Andy?) then see the \texttt{.pdf} version.
\item
  We still need to discuss authorship and order of authorship.
\end{itemize}

\newpage

@@

\bigskip

Sean C. Anderson\textsuperscript{1*}, Jonathan W. Moore\textsuperscript{1}, Nicholas K. Dulvy\textsuperscript{1}, Andrew B. Cooper\textsuperscript{2} (Michelle M. McClure?, Trevor A. Branch?, Authors and order to be discussed)

@@

@@

A diversified financial portfolio reduces risk by exploiting the covariance between assets --- ideally one stocks rises while another one falls --- and two key mechanisms can generate such asynchrony in metapopulation dynamics. First, localized habitat features can filter the environment generating unique conditions for subpopulations \citep{schindler2008, rogers2008} (\emph{senu} the Moran effect). However, since many salmon species spend considerable time in a shared ocean environment \citep{quinn2005}, a second mechanism is also important --- diversity of response to the environment \citetext{\citealp[i.e.~response diversity,][]{elmqvist2003}; \citealp[and biocomplexity][]{colwell1998}; \citealp{hilborn2003}}. This mechanism can result from unique phenotypic or genetic traits \citep{crozier2008, kovach2012} and be derived from rapid contemporary adaption \citep{stockwell2003, fraser2011} or long-term evolution to historical conditions \citep{eliason2011}. In this paper we focus on this latter, response-diversity mechanism, and evaluate it in the context of thermal response diversity.

Salmon are strongly affected by climate warming and yet show a remarkable diversity of tolerance to temperature \citep{beacham1989, crozier2006, crozier2008}. In addition to climate warming posing perhaps the greatest threat to global biodiversity \citep{thomas2004}, warming poses a particular threat to riverine species whose ranges are largely confined to existing habitat \citep{thomas2010} and where shallower water, compared to larger water basins, can be affected more rapidly by thermal changes \citep{isaak2010} and by snow-melt timing and extreme hydrological events \citep{crozier2008}. These consequences, and in particular warmer water itself, can combine to limit salmon productivity through, for example, oxygen limitation \citep{portner2007} leading to decreased cardiac performance \citep{eliason2011} and having profound implications for behaviour \citep{goniea2006}, disease resistance \citep{crozier2008}, energetic costs in general \citep{rand1998}, and ultimately survival \citep{peterman1998, eliason2011}. With 29\% of Pacific Northwest salmon populations having gone extinct since Euro-American contact \citep{gustafson2007}, these populations are at risk from any further decline in fitness \citep{mcclure2003}. Yet, adverse stream temperatures are already impeding recovery of some PNW salmon populations \citep{mccullough1999} and are expected to make recovery targets more difficult to achieve \citep{battin2007}.

@@

where $i$ represents a population, $t$ a generation time, $R$ the number of returns, $S$ the number of spawners, $a$ the productivity parameter (which can vary with the environment), and $b$ the density-dependent term (which is used as the asset weights in the portfolios). The term $w_{i(t)}$ represents first-order autocorrelated error. Formally, $w_{i(t)} = w_{ti-1} \rho_w + r_{i(t)}$, where $r_{i(t)}$ represents independent and normally distributed error with mean 0 and standard deviation of $\sigma_r$ (0.3; we include the base values in parentheses after relevant parameters). The parameter $\rho_w$ (0.4) represents the correlation between residuals from subsequent generations.

@@

where $W_i$ controls the width of the curve for population $i$, $e_t$ represents the environmental value at generation $t$, $e_i^{\mathrm{opt}}$ represents the optimal temperature for population $i$, and $a_i^{\mathrm{max}}$ represents the maximum possible $a$ value for population $i$. We set the $W_i$ parameters (evenly spaced values increasing and decreasing between 0.05 and 0.02) and calculated the $a_i^{\mathrm{max}}$ parameters so that the area under each curve was equal (30 units). We chose parameter values such that some populations were warm-tolerant, some were cold-tolerant, and some had a wider range of thermal-tolerance, but a lower maximum productivity (see Fig.~2a). Although we refer to a thermal-tolerance curve because temperature is a dominant driver of salmonid performance \citep{mccullough1999}, our model applies to any environmental tolerance (e.g.~tolerance to stream flow volume or changes in snow melt timing \citep{crozier2008}).

@@

where $R_{j(t)}$ is the number of returning salmon at generation $t$ whose natal stream was stream $j$. The subscript $k$ represents a stream ID and $n$ the number of populations. The denominator is a normalizing constant to ensure the desired fraction of fish stray. See Figure \ref{f:stray} for an example straying matrix.

Our simulation did not account for the homogenization of diversity due to straying. For example, all salmon in one population maintained the same thermal-tolerance curve regardless of how many salmon it received from another stream. However, the low straying rates in our simulation rate should render this effect minimal except for populations at low abundance. In our model, the main implication is that, in reality, populations that reach a low abundance may reach demographic extinction, potentially suffer consequences such as inbreeding depression \citep{wang2002} and subsequently contribute little to response diversity.

@@

where $A$ represents the return abundance and $a$ and $b$ represent the Ricker model parameters. We included implementation uncertainty in the actual harvest rate $H_{\mathrm{act}}$ as

@@

where $\alpha_h$ and $\beta_h$ are the location and shape parameters in a beta distribution. They can be calculated from the desired mean $H_{\mathrm{tar}}$ and standard deviation $\sigma_h$ (0.05) as \citep[p.~97]{morgan1990}

@@

Further, to establish a range of spawner-return values and to mimic the start of an open-access fishery, for the first 30 years we drew the fraction of fish harvested randomly from a uniform distribution between 0.1 and 0.9. We discarded these initial 30 years as a burn-in period.

@@

where $e_t$ represents the environmental value in generation $t$ and $d$ represents normally distributed deviations of mean 0 and standard deviation $\sigma_d$ (2). We represented long-term environmental dynamics as a linear shift in the environmental value through time

@@

where $\beta_e$ (0.114) represents the slope. To maintain a balanced response, we centered the trend by subtracting the mean $\overline{\beta_e t}$ so that midway through the simulation (after any burn-in period) the environmental value was at the mean environmental tolerance.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Conserve an even sampling of response diversity.
\item
  Conserve the middle section of the metapopulation (conserve stable populations).
\item
  Conserve the lower half of the metapopulation (conserve cool-tolerant populations).
\item
  Conserve the upper half of the metapopulation (conserve warm-tolerant populations).
\end{enumerate}

@@

\subsection{Implications for salmon conservation}

@@

Existing salmon management structures in the US and Canadian PNW support a portfolio conservation perspective. In the US, Evolutionarily Significant Units (ESUs) represent salmon populations that are reproductively isolated with an evolutionary heritage \citep{waples1991, moritz1994} and finer-scale Viable Salmonid Populations (VSPs) represent groups of fish that spawn in a given lake or stream in a particular season \citep{mceacheran2000}. In Canada, the rough equivalent to the ESU is a Conservation Unit (CU) as defined by the Wild Salmon Policy \citep{dfo2005wsp}. A CU consists of a group of salmon that are reproductively isolated and that if lost would be unlikely to recolonize in a reasonable time frame \citep{dfo2005wsp}. Both the US and Canadian guidelines recognize still-finer-scale population structure. We suggest that a salmon portfolio in our model could represent an ESU or CU and that the lessons learned from our models are thus directly applicable to management guidelines in the PNW.

\emph{To be incorporated?} Some VSP guidelines \citep{mceacheran2000} that are line with our findings\ldots{}

\begin{itemize}
\item
  maintaining diversity of a variety of forms to buffer against short-term environmental changes and adaptation to long-term environmental changes
\item
  conservation efforts should not focus exclusively where there is currently an abundance of salmon
\item
  metapopulation (multiple populations with some exchange) are important to maintain
\item
  some should be close for straying, but some should be far apart to reduce risk from sudden environmental change
\item
  important to incorporate uncertainty of ESU-level processes into assessments
\item
  CU guidelines \citep{dfo2005wsp} suggest\ldots{}
\end{itemize}

Our model complements other simulation-based salmon-habitat prioritization models. While these other models tend to focus on detailed assessment of individual fish stocks, our model is unique as the first to consider the role of response diversity in buffering risk for metapopulations as a whole. The Shiraz model \citep{scheuerell2006} is one complementary prioritization scheme. It focuses on detailed conditioning of the habitat-population-dynamics relationship at multiple life-history stages for a single salmon population. Whereas the Shiraz model can be applied to an entire watershed, it combines the populations together as a single unit. A second salmon prioritization model proposes combining population viability measures with an assessment of the genetic consequences of losing particular populations \citep{allendorf1997}. This model, however, also focuses on the assessment of individual stocks without considering their covariance and therefore the performance of the salmon portfolio as a whole. Our model does not replace these prioritization schemes. Rather, it proposes an additional focus on prioritization that optimizes metapopulation risk and growth across plausible environmental scenarios while being robust to numerous sources of uncertainty.

\subsection{Broad implications, research extensions, and priorities}

Our results emphasize the importance of thinking at the portfolio level when making conservation decisions --- considering aggregate risk and performance for ecological portfolios. Although our results may appear intuitive, we often don't often consider aggregate risk and only by simultaneously considering aggregate risk and return can we optimally diversify ecological systems \citep{ando2012}. Thus we can think of portfolio risk-return performance as another dimension of conservation. This dimension emphasizes the value of a broader scale of management and focussing not just on currently productive populations but also on less productive populations to reduce long-term aggregate risk \citep[e.g.][]{hilborn2003, price2008}. This perspective does not negate an understanding at a finer scale, say of individual fish stocks. Rather, as in finance, it requires both an understanding of stock performance and an assessment of their covariance to predict properties of the portfolio as a whole.

We suggest a number of specific extensions to our simulation model. First our model could be extended beyond thermal response diversity. For salmon this might include response diversity to interdecadal climate signals such as the Pacific Decadal Oscillation \citep{mantua2002}, or to stream flow and dissolved oxygen \citep{priede1988}. Second, our model could be extended to metapopulations of other taxa, to ecological communities (after accounting for species interactions), or to meta-communities. Third, an extension of our model would consider the Moran or environmental-filter concept \citep{schindler2008, rogers2008} where populations experience increasingly different environmental forces at further distances. Fourth, a model could consider the contribution of contemporary evolution \citep{stockwell2003}. This rapid adaptation to changes in the environment could strongly affect portfolio performance and emphasizes the importance of maintaining genetic diversity. Finally, our model could be conditioned on a system of interest --- a particular river basin for example --- and the metapopulation portfolio could be optimized across conservation and restoration options as part of a formal decision analysis.

@@

In conclusion, our results demonstrate the utility of considering metapopulations in a portfolio context and the power of portfolio simulation to consider management strategies that minimize metapopulation risk and maximize growth under uncertain environmental conditions. Our findings show that response diversity buffers metapopulation risk given short-term environmental stochasticity and ensures persistence given longterm regime changes. Further, our findings show that, independent of response-diversity, conserving more populations buffers metapopulation risk. These results point to the critical importance of choosing management, conservation, and restoration actions that preserve and promote response diversity and are robust to our uncertainty about the distribution of response diversity and future climatic conditions.

@@

\includegraphics[height=5.5in]{../examples/simulation-diagram3.pdf}

@@

\includegraphics[width=2.9in]{../examples/thermal-curve-scenarios.pdf}

@@

\includegraphics[width=4.0in]{../examples/spatial-arma-sim.pdf}

@@

\includegraphics[width=4.7in]{../examples/spatial-mv.pdf}

@@

\includegraphics[width=5.0in]{../examples/cons-plans-n.pdf}

### 2013-08-26 inst/ms/salmonfolios.tex
Updates to ms; wrap ms

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[round]{natbib}
\bibpunct{(}{)}{;}{a}{}{;}
\textheight 20.5cm
\usepackage{lineno}
\usepackage{xcolor}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}

@@

\hyphenation{meta-pop-ulation meta-pop-ulations sub-pop-ulations sub-pop-ulation e-con-o-mist}

@@

\linenumbers
\modulolinenumbers[2]
\begin{spacing}{1.5}
\include{ms}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[round]{natbib}
\bibpunct{(}{)}{;}{a}{}{;}
%\textheight 20.5cm
%\topmargin -1.43cm
%\oddsidemargin 1.2cm
%\evensidemargin 1.2cm
%\textwidth 14.5cm
\usepackage{lineno}
\usepackage{xcolor}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}

\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{-6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{-6pt plus 2pt minus 2pt}

\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
\setsansfont{Calibri}
\setmonofont{Inconsolata}
\setmainfont{Minion Pro}

@@

\hyphenation{meta-pop-ulation meta-pop-ulations sub-pop-ulations sub-pop-ulation e-con-o-mist en-vi-ron-men-tal pri-or-i-ti-za-tion}

@@

\linenumbers
\modulolinenumbers[2]
\begin{spacing}{1.4}
\setlength{\parskip}{12pt}
\setlength{\parindent}{0cm} 
\include{ms}
